\section{Large Scale Program}
\subsection{Program Structure}
\begin{frame}{Seperate .cpp files}
  \begin{itemize}
    \item As the size of the program grows, it takes more and more time to compile.
    \item It also difficult to understand the overall structure of the program.\pause
    \item A good way is to seperate the program into different parts. 
    \item When compiling, we only need to compile the modified parts and then link them together.
    \item The seperation of the program is also a good way to make the program easier to understand.
  \end{itemize}
\end{frame}
\begin{frame}[fragile]{Seperate .hpp files}
  Suppose we have two functions and we want to put them into two different files.
  \begin{cpp}
    // A.cpp
    void do_something() {
      do_something_else();
    }
    // B.cpp
    void do_something_else() {
      // do things here...
    }
      \end{cpp}
    But this code will not compile, because in A.cpp, \texttt{do\_something\_else()} is not defined.
\end{frame}

\begin{frame}[fragile]{Seperate .hpp files}
  To solve this problem, we can put the declaration into another file, and include it when needed.
  \begin{columns}
    \begin{column}{0.5\linewidth}
      \begin{cpp}
// A.hpp
void do_something();
// A.cpp
#include "A.hpp"
#include "B.hpp"
void do_something() {
  do_something_else();
}
      \end{cpp}
    \end{column}
    \begin{column}{0.5\linewidth}
      \begin{cpp}
// B.hpp
void do_something_else();
// B.cpp
#include "B.hpp"
void do_something_else() {
  // do things here...
}
      \end{cpp}
    \end{column}
    \end{columns}
\end{frame}
\begin{frame}[fragile]{Header Guard}
  To avoid including the same header file multiple times, we should write header guard in each header file.
  \begin{cpp}
// In My_Class.hpp
#ifndef MY_CLASS_HPP 
#define MY_CLASS_HPP
    // ...
#endif // MY_CLASS_HPP
  \end{cpp}
\end{frame}
\begin{frame}[fragile]{Deal with Templates}
  What if we want to put the declarations and implementations in different files?\pause 
  \begin{columns}
    \begin{column}{0.5\linewidth}
      \begin{cpp}
template<typename Tp>
class Foo{
 public:
  Foo(Tp data);
  void bar();
 private: 
  Tp data_;
}
#include "foo.inc"
      \end{cpp}
      foo.hpp
    \end{column}
    \begin{column}{0.5\linewidth}
      \begin{cpp}
template<typename Tp>
Foo<Tp>::Foo(Tp data) 
  : data_(data) {}

template<Typename Tp>
void Foo<Tp>::bar() {
  std::cout << data_ 
            << std::endl;
}
      \end{cpp}
      foo.inc
    \end{column}
  \end{columns}
Include the implementation file at the end of the header file.\\
\end{frame}
\subsection{Name Spaces}
\begin{frame}{What is Name Space}
  \begin{itemize}
    \item A namespace is a declarative region that provides a scope to the identifiers (names of the types, function, variables etc.) inside it.
    \item \texttt{std} is the standard namespace.
    \item To refer to an identifier in the namespace, use \texttt{::}. (e.g. \texttt{std::vector})
  \end{itemize}
\end{frame}
\begin{frame}{Why we need it}
  \begin{itemize}
    \item Namespace provide a method for preventing name conflicts in large projects.
    \item Do not write \texttt{using namespace} directly, especially not in a header file. This will reintroduce the name conflict into your code. 
    
  \end{itemize}
\end{frame}
\begin{frame}{The Interface Principle}
  For a class X, all functions, including free functions, that both
    \begin{itemize}
    \item[(a)] "mention" X, and
    \item[(b)] are "supplied with" X
    \end{itemize}
    are logically part of X, because they form part of the interface of X. 
    \begin{itemize}
      \item Putting the functions and the classes into the same namespace is a good way to do the seperation. Just like packages in Python.
    \end{itemize}
\end{frame}
\begin{frame}[fragile]{Defining a Namespace}
\begin{columns}
  \begin{column}{0.5\linewidth}
    \begin{cpp}
// declare a namespace
namespace ShanghaiTech {
  class SIST_Student {/* */}
  void debug_programs(SIST_Student &);
  class SLST_Student {/* */}
  void write_paper(SLST_Student &);
  // ...
}
   \end{cpp}
  \end{column}
  \begin{column}{0.5\linewidth}
  \begin{cpp}
#include "ShanghaiTech.hpp"
// open the namespace
namespace ShanghaiTech {
  /* The definations of the classes and functions */
}
  \end{cpp}
  \end{column}
\end{columns}
\begin{columns}
  \begin{column}{0.5\linewidth}
    ShanghaiTech.hpp
  \end{column}
  \begin{column}{0.5\linewidth}
    ShanghaiTech.cpp
  \end{column}
\end{columns}
\end{frame}
